Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-08-01 Paper/tool.tex
small typo changes

% Chokepoint calculation
\par Once \toolname{} generates the routing trees, they can be processed to
determine chokepoint potentials or by other researchers interested in other questions. To calculate chokepoint potential, \toolname{} iterates over every path
between each AS-pair. Because we use the same random tie-break method as BGPSim,this process returns 
exactly one path between each AS-pair considered, even if multiple options exist in the
routing tree. Tiebreaks do not have a noticeable effect on our results. For instance, the maximum
standard deviation for the chokepoint potential of any AS in 5 runs of one of our timestamps was 
$\leq$ 0.005, meaning the chokepoint potentials for each AS barely changed depending on the tiebreak
decisions.
Once the path has been determined, it is traversed to identify border nodes and increment their counts, both
for outgoing and incoming paths.  Thus, only one traversal is conducted
per path. Additionally, the number of paths of each type that belong to each
nation is tallied. \toolname{} takes the resulting chokepoint
potentials and generates national chokepoint potentials for each nation.

>>>>

% Chokepoint calculation
\par Once \toolname{} generates the routing trees, they can be processed to
determine chokepoint potentials or by other researchers interested in other questions. To calculate chokepoint potential, \toolname{} iterates over every path
between each AS-pair. Because we use the same random tie-break method as BGPSim, this process returns 
exactly one path between each AS-pair considered, even if multiple options exist in the
routing tree. Tiebreaks do not have a noticeable effect on our results. For instance, the maximum
standard deviation for the chokepoint potential of any AS in 5 runs of one of our timestamps was 
$\leq$ 0.005, meaning the chokepoint potentials for each AS barely changed depending on the tiebreak
decisions.
Once the path has been determined, it is traversed to identify border nodes and increment their counts, both
for outgoing and incoming paths.  Thus, only one traversal is conducted
per path. Additionally, the number of paths of each type that belong to each
nation is tallied. \toolname{} takes the resulting chokepoint
potentials and generates national chokepoint potentials for each nation.
